Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
hscc17

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.  Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sample and hold
processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  This pulse transfer function can be
computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$.
%
\end{myassumption}

>>>>

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretized to obtain the
discrete equivalent coefficients $b$ and $a$~\cite{Astrom08} via ZOH
discretization.

\red{[why do we discuss the ZOH at this point?]}

Although there are several discretization methods available
in the literature~\cite{Franklin15}, the zero-order hold (ZOH)
discretization is more suitable for representing the sample and hold
processes that are typically employed in complex systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization
models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma}\cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the
output sampled by an ADC and the digital input provided by the ZOH.  It is equivalent at the sample times ({\it i.e.}, $t=kT$) to the continuous transfer
function $G(s)$ driven by ZOH.  
\red{[what does it mean that it is continuous ``at the sample times''? We're working in frequency. Are you matching poles? There is still no clear relationship between continuous and samples transfer functions, it is not formal in my opinion.]}
This pulse transfer function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}
%
For the sake of brevity, 
we will use the notation $G(z)$ to represent the pulse transfer function.
%
\end{mylemma}

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $\tilde u(k)$ \red{[is this a new notation over the time domain? It does not reflect the signals used in the plot -- utterly confusing!]} at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$.
%
\end{myassumption}
